\chapter{Introduction}
As of 2023, a compound annual growth rate of 10\% was forecast for the world used car market between 2024 and 2029.
There are a lot of factors that may cause such a significant growth, including shorter vehicle ownership times, changes in preferences for cars, and increasing flexibility of supply \autocite{UsedCarMarket}.
The market growth and upward trend in the demand for cost-effective used cars \autocite{EuropeUsedCar} raise the necessity of proper price calculations for resale cars, since it affects both car dealers and clients.
It should estimate the accurate value of the vehicle based on its condition. Moreover, the initial set price of the car is significant for the final revenue received from the dealership.

This paper addresses the business problem of determining competitive prices for used cars to be advertised.
For the accuracy of the analysis, only one car model was chosen: the \ac{vw} Golf, as it is one of the most popular cars on used car market in such countries as Germany, Belgium, Italy and others \autocite{misselhornDevelopmentUsedCar2024}.
The following research questions were posed: 
\newline
 1) What factors influence \ac{vw} Golf's price the most? \newline
 2) What is the price the \ac{vw} Golf should be advertised for?\newline
To answer the questions, correlation and linear regression were calculated, and the model has been created. The programs used for the analysis are \ac{excel} and Orange.
The research was based on a large-scale dataset for automotive applications, which contained various data for 0.25 million used cars in the United Kingdom. For research purposes, only a part about used car advertisements was used.

